% \section{Overview}
\section{概览}

% The Zone.js project provides multiple asynchronous execution contexts running within
% a single JavaScript thread (i.e. within the main browser UI thread or within a single
% web worker). Zones are a way of sub-dividing a single thread using the JavaScript
% event loop. A single zone does not cross thread boundaries. A nice way to think about
% zones is that they sub-divide the stack within a JavaScript thread into multiple mini-
% stacks, and sub-divide the JavaScript event loop into multiple mini event loops that
% seemingly run concurrently (but really share the same VM event loop). In effect,
% Zone.js helps you write multithreaded code within a single thread.

Zone.js 项目提供了在单个 JavaScript 线程中运行多个异步执行上下文
（即主浏览器 UI 线程或单个 web worker 中）。
Zone 使用了将 JavaScript 事件循环分割单个线程的方式。
单个 zone 不会跨越线程边界。
考虑 zone 的良好方法是它们将 JavaScript 线程内的栈分割成多个小栈，
并将 JavaScript 事件循环分划分为多个小的事件循环，
这些循环似乎同时运行（但却共享相同的 VM 事件循环）。
实际上，Zone.js 有助于你在单线程中编写多线程代码。

% When Zone.js is loaded by your app, it monkey-patches certain asynchronous calls
% (e.g.
% \texttt{setTimer}
% ,
% \texttt{addEventListener}
% ) to implement zone functionality. Zone.js does
% this by adding wrappers to the callbacks the application supplies, and when a timeout
% occurs or an event is detected, it runs the wrapper first and then the application
% callback. Chunks of executing application code form tasks and each task executes in
% the context of a zone. Zones are arranged in a hierarchy and provide useful features
% in areas such as error handling, performance measuring and executing configured
% work items upon entering and leaving a zone (all of which might be of great interest
% to implementors of change detection in a modern web UI framework, like Angular).

当你的应用程序加载 Zone.js 时，
它会修补某些异步调用（例如 \texttt{setTimer}、\texttt{addEventListener}）来实现 zone 功能。
Zone.js 通过向应用提供的回调函数添加包装器做到这点，
当超时或检测到事件时，它首先运行包装器，然后运行回调。
执行应用程序代码形成任务的块，每个任务在 zone 的上下文。
Zones 按层次排列并提供有用的功能在错误处理、性能测量和执行配置等领域进入和离开 zone 时的工作项目
（所有这些对自己实现现代 Web UI 框架中变更检测有参考价值）。

% Zone.js is mostly transparent to application code. Zone.js runs in the background and
% for the most part “just works”. For example, Angular uses Zone.js and Angular
% application code usually runs inside a zone. Tens of thousands of Angular application
% developers have their code execute within zones without evening knowing these exist.
% More advanced applications can have custom code to make zone API calls if needed
% and become more actively involved in zone management. Some application
% developers may wish to take certain steps to move some non-UI performance-critical
% code outside of the Angular zone – using the
% \href{https://next.angular.io/api/core/NgZone}{NgZone}
% class).

Zone.js 对应用代码大多是透明的。Zone.js 在后台运行，大部分“只是默默工作”。
例如，Angular 使用 Zone.js，Angular 应用代码通常运行在 zone 内。
成千上万的 Angular 应用开发人员甚至都没意识到这点。
如果有需要，可以自定义 zone API 调用，手动管理 zone 的运行。
有些应用开发人员可能希望采取某些步骤将非 UI 性能关键代码移出 Angular zone ——
这时可以使用 \href{https://next.angular.io/api/core/NgZone}{NgZone} 类。

\input{1_internals_of_zone_js/1_0_0_project_information.tex}
