% \section{Using Zone.js}
\section{使用 Zone.js}

% Before looking in detail at how Zone.js itself is implemented, we will first look at how
% it is used in production, using the example of the very popular Angular project.

在详细了解 Zone.js 自身是如何实现之前，我们首先了解在生产中如何使用它，
这里以非常流行的 Angular 项目为例。

% The use of Zone.js with Angular is optional, but used by default. Use of zones is
% mostly a good idea but there are some scenarios (e.g. using Angular Elements to build
% Web Compoenents) when this is not the case.

在 Angular 中使用 Zone.js 是可选的，不过却是默认开启。
使用 zones 通常来说是个好主意，
但存在某些场景（比如，使用 Angular Elements 构建 Web Compoenents）下是不必要的。

% To use Zone.js in your applications, you need to load it. Your package.json file will
% need (if creating a project using Angular CLI, this is added automatically for you):

要在你的应用中使用 Zone.js，你需要加载它。在 package.json 中写入
（如果你的项目是通过 Angular CLI 创建，会自动帮你添加进去）：

\input{../output/1_internals_of_zone_js/code/1_1_0.tex}

% You should load Zone.js after loading core.js (if using that). For example, if using an
% Angular application generated via Angular CLI (as most production apps will be),
% Angular CLI will generate a file called <project-name>/src/polyfills.ts and it will
% contain:

你应该在加载 core.js 之后加载 Zone.js（如果用到了它）。
例如，如果你使用 Angular CLI 生成 Angular 应用（就像大多数生产应用一样），
Angular CLI 将生成一个名为 <project-name>/src/polyfills.ts 的文件，它将包含：

\input{../output/1_internals_of_zone_js/code/1_1_1.tex}

% Angular CLI also generates an angular.json configuration file, with this line that sets
% up polyfills:

Angular CLI 还会生成一个 angular.json 配置文件，该行设置 polyfills：

\input{../output/1_internals_of_zone_js/code/1_1_2.tex}

% If writing your application in TypeScript (recommended), you also need to get access
% to the ambient declarations. These define the Zone.js API and are supplied in:

如果你的应用是用 TypeScript（推荐）编写的，
您还需要配置声明访问。 这些定义了 Zone.js API 并在以下位置提供：

\begin{itemize}
  \item \href{https://github.com/angular/zone.js/blob/master/dist/zone.js.d.ts}
        {<ZONE-MASTER>/dist/zone.js.d.ts}
\end{itemize}

% (IMPORTANT: This file is particularly well documented and well worth some careful
% study by those learning Zone.js). Unlike declarations for most other libraries,
% zone.js.d.ts does not use
% \texttt{import}
% or
% \texttt{export}
% at all (those constructs do not appear
% even once in that file). That means application code wishing to use zones cannot
% simply import its .d.ts file, as is normally the case. Instead, the
% \texttt{///reference}
% construct needs to be used. This includes the referenced file at the site of the
% \texttt{///reference}
% in the containing file. The benefit of this approach is that the containing
% file itself does not have to (but may) use
% \texttt{import}
% , and thus may be a script, rather
% than having to be a module. The use of zones is not forcing the application to use
% modules (however, most larger applications, including all Angular applications - will).
% How this works is best examined with an example, so lets look at how Angular
% includes zone.d.ts. Angular contains a file, types.d.ts under its packages directory
% (and a similar one under its modules directory and tools directory):

（注意：这个文件有着良好的文档说明，值得那些了解 Zone.js 的人仔细学习）。
不同于其它库的声明文件，zone.js.d.ts 根本不使用 \texttt{import} 或 \texttt{export}
（那些命令甚至没有出现在那个文件中一次）。
这意味着通常情况下，希望使用 zones 的应用代码不能只简单地导入其\, .d.ts 文件。
相反，应该使用 \texttt{///reference} 命令。
这包括网站上的参考文件 \texttt{///reference} 包含文件中的引用。
这种方法的好处是包含文件本身不必（但可以）使用 \texttt{import}，因此可能是一个脚本，
相比与其必须是一个模块。
使用 zones 并不强制应用程序使用模块（然而，大多数大型应用，包括所有 Angular 应用会使用）。
最好通过一个例子来研究它是如何工作的，
所以让我们看看 Angular 是如何包括 zone.d.ts。 Angular 包含一个文件，
types.d.ts 在包目录下（在它的模块目录和工具目录下有一个类似的）。

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/modules/types.d.ts}
        {<ANGULAR-MASTER>/packages/types.d.ts}
\end{itemize}

% and it has the following contents:

它包含如下内容：

\input{../output/1_internals_of_zone_js/code/1_1_3.tex}

\input{1_internals_of_zone_js/1_1_0_use_within_angular.tex}
