\section{API Model}

Zone.js exposes an API for applications to use in the
\href{https://github.com/angular/zone.js/blob/master/dist/zone.js.d.ts}
{<ZONE-MASTER>/dist/zone.js.d.ts}
file.

The two main types it offers are for tasks and zones, along with some helper types. A
zone is a (usually named) asynchronous execution context; a task is a block of
functionality (may also be named). Tasks run in the context of a zone.

Zone.js also supplies a const value, also called
\texttt{Zone}
, of type
\texttt{ZoneType}
:

\input{1_internals_of_zone_js/code/1_2_0.tex}

Recall that TypeScript has distinct declaration spaces for values and types, so the
\texttt{Zone}
value is distinct from the
\texttt{Zone}
type. For further details, see the TypeScript
Language Specification – Section 2.3 – Declarations:

\begin{itemize}
  \item \url{https://github.com/Microsoft/TypeScript/blob/master/doc/spec.md#2.3}
\end{itemize}

Apart from being used to define the
\texttt{Zone}
value,
\texttt{ZoneType}
is not used further.

When your application code wishes to find out the current zone it simply uses
\texttt{Zone.current}
, and when it wants to discover the current task within that zone, it
uses
\texttt{Zone.currentTask}
. If you need to figure out whether Zone.js is available to your
application (it will be for Angular applications), then just make sure
\texttt{Zone}
is not
undefined. If we examine:

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/core/src/zone/ng_zone.ts}
        {<ANGULAR-MASTER>/packages/core/src/zone/ng\_zone.ts}
\end{itemize}

– we see that is exactly what Angular’s NgZone.ts does:

\input{1_internals_of_zone_js/code/1_2_1.tex}

Two simple helper types used to define tasks are
\texttt{TaskType}
and
\texttt{TaskData}
.
\texttt{TaskType}
is just a human-friendly string to associate with a task. It is usually set to one of the
three task types as noted in the comment:

\input{1_internals_of_zone_js/code/1_2_2.tex}

\texttt{TaskData}
contains a boolean (is this task periodic, i.e. is to be repeated) and two
numbers - delay before executing this task and a handler id from
\texttt{setTimout}
.

\input{1_internals_of_zone_js/code/1_2_3.tex}

A task is an interface declared as:

\input{1_internals_of_zone_js/code/1_2_4.tex}

There are three marker interfaces derived from
\texttt{Task}
:

\input{1_internals_of_zone_js/code/1_2_5.tex}

The comments for Task nicely explains their purpose:

\input{1_internals_of_zone_js/code/1_2_6.tex}

There are three helper types used to define
\texttt{Zone}
.
\texttt{HasTaskState}
just contains
booleans for each of the task types and a string:

\input{1_internals_of_zone_js/code/1_2_7.tex}

\texttt{ZoneDelegate}
is used when one zone wishes to delegate to another how certain
operations should be performed. So for forcking (creating new tasks), scheduling,
intercepting, invoking and error handling, the delegate may be called upon to carry
out the action.

\input{1_internals_of_zone_js/code/1_2_8.tex}

\texttt{ZoneSpec}
is an interface that allows implementations to state what should have when
certain actions are needed. It uses
\texttt{ZoneDelegate}
and the current zone:

\input{1_internals_of_zone_js/code/1_2_9.tex}

The definition of the
\texttt{Zone}
type is:

\input{1_internals_of_zone_js/code/1_2_10.tex}

\input{1_internals_of_zone_js/1_2_0_relationship_between_zone_zonespec_zonedelegate_interfaces.tex}

\input{1_internals_of_zone_js/1_2_0_relationship_between_zone_zonespec_zonedelegate_interfaces.tex}
