% \subsection{zone.ts}
\subsection{zone.ts}

% The first six hundred lines of the zone.ts file is the well-commented definition of the
% Zone.js API, that will end up in zone.d.ts. The slightly larger remainder of the file is an
% implementation of the
% \texttt{Zone}
% const:

zone.ts 的前 600 行代码是注释良好的 Zone.js API 定义，最后会导出到 zone.d.ts。
文件稍大的剩余部分是 \texttt{Zone} const 的实现：

\input{../output/1_internals_of_zone_js/code/1_4_0_0.tex}

% The
% \texttt{\_ZonePrivate}
% interface defines private information that is managed per zone:

\texttt{\_ZonePrivate} 接口定义了管理每个 zone 的私有信息：

\input{../output/1_internals_of_zone_js/code/1_4_0_1.tex}

% When using the client API you will not see this, but when debugging through the
% Zone.js implementation, it will crop up from time to time.

当使用客户端 API 时是不会看到这些的，但当你调试 Zone.js 的实现时候，它会不时的出现。

% A microtask queue is managed, which requries these variables:

管理微任务队列，需要如下变量：

\input{../output/1_internals_of_zone_js/code/1_4_0_2.tex}

% \texttt{\_microTaskQueue}
% is an array of microtasks, that must be executed before we give up
% our VM turn.
% \texttt{\_isDrainingMicrotaskQueue}
% is a boolean that tracks if we are in the
% process of emptying the microtask queue. When a task is run within an existing task,
% they are nested and
% \texttt{\_nativeMicroTaskQueuePromise}
% is used to access a native
% microtask queue. Which is stored as a global is not set. Two functions manage a
% microtask queue:

\texttt{\_microTaskQueue} 是一个微任务数组，这必须在我们放弃 VM 轮转之前执行。
\texttt{\_isDrainingMicrotaskQueue} 是一个布尔值，用于跟踪我们是否处于清空微任务队列的过程
当一个任务运行在一个已经存在的任务时，它们是嵌套着，
\texttt{\_nativeMicroTaskQueuePromise} 用于获取一个原生微任务队列。
以下两个函数用于管理微任务队列：

\begin{itemize}
  \item scheduleMicroTask
  \item drainMicroTaskQueue
\end{itemize}

% It also implements three classes:

它还实现了三个类：

\begin{itemize}
  \item Zone
  \item ZoneDelegate
  \item ZoneTask
\end{itemize}

% There are no implementations of
% \texttt{ZoneSpec}
% in this file. They are in the separate zone-
% spec sub-directory.

该文件没有关于 \texttt{ZoneSpec} 的实现。
他们在单独的 zone-spec 子目录中。

% \texttt{ZoneTask}
% is the simplest of these classes:

\texttt{ZoneTask} 是这些类中最简单的：

\input{../output/1_internals_of_zone_js/code/1_4_0_3.tex}

% The constructor just records the supplied parameters and sets up
% \texttt{invoke}
% :

构造函数只记录提供的参数并设置 \texttt{invoke}：

\input{../output/1_internals_of_zone_js/code/1_4_0_4.tex}

% The interesting activity in here is setting up the
% \texttt{invoke}
% function. It increments the
% \texttt{\_numberOfNestedTaskFrames}
% counter, calls
% \texttt{zone.runTask()}
% , and in a
% \texttt{finally}
% block,
% checks if
% \texttt{\_numberOfNestedTaskFrames}
% is 1, and if so, calls  the standalone function
% \texttt{drainMicroTaskQueue()}
% , and then decrements
% \texttt{\_numberOfNestedTaskFrames}
% .

这里有趣的活动是设置 \texttt{invoke} 函数。
它递增 \texttt{\_numberOfNestedTaskFrames} 计数器，调用 \texttt{zone.runTask()}，
并在 \texttt{finally} 块中检查 \texttt{\_numberOfNestedTaskFrames} 是否为 1，
如果是，则调用独立函数 \texttt{drainMicroTaskQueue()}，
然后递减 \texttt{\_numberOfNestedTaskFrames} 计数器。

\input{../output/1_internals_of_zone_js/code/1_4_0_5.tex}

% A custom
% \texttt{toString()}
% implementation returns
% \texttt{data.handleId}
% (if available) or else the
% object’s
% \texttt{toString()}
% result:

一个自定义的 \texttt{toString()} 返回 \texttt{data.handleId}（如果可用）
或者对象 \texttt{toString()} 的结果。


\input{../output/1_internals_of_zone_js/code/1_4_0_6.tex}

% \texttt{drainMicroTaskQueue()}
% is defined as:

\texttt{drainMicroTaskQueue()} 定义如下：

\input{../output/1_internals_of_zone_js/code/1_4_0_7.tex}

% The
% \texttt{\_microTaskQueue}
% gets populated via a call to
% \texttt{scheduleMicroTask}
% :

\texttt{\_microTaskQueue} 通过调用 \texttt{scheduleMicroTask} 来填充：

\input{../output/1_internals_of_zone_js/code/1_4_0_8.tex}

If needed (not running in a task), this calls
\texttt{setTimeout}
with timeout set to 0, to
enqueue a request to drain the microtask queue. Even though the timeout is 0, this
does not mean that the
\texttt{drainMicroTaskQueue()}
call will execute immediately.
Instead, this puts an event in the JavaScript’s event queue, which after the already
scheduled events have been handled (there may be one or move already in the
queue), will itself be handled. The currently executing function will first run to
completion before any event is removed from the event queue. Hence in the above
code, where
\texttt{scheduleQueueDrain()}
is called before
\texttt{\_microTaskQueue.push()}
, is not
a problem.
\texttt{\_microTaskQueue.push()}
will execute first, and then sometime in future,
the
\texttt{drainMicroTaskQueue()}
function will be called via the timeout.

% The
% \texttt{ZoneDelegate}
% class has to handle eight scenarios:

\texttt{ZoneDelegate} 类必须处理八个场景：

\begin{itemize}
  \item fork
  \item intercept
  \item invoke
  \item handleError
  \item scheduleTask
  \item invokeTask
  \item cancelTask
  \item hasTask
\end{itemize}

% It defines variables to store values for a
% \texttt{ZoneDelegate}
% and
% \texttt{ZoneSpec}
% for each of
% these, which are initialized in the constructor.

它定义了变量来存储每个 \texttt{ZoneDelegate} 和 \texttt{ZoneSpec} 的值，这些值在构造函数中初始化。

\input{../output/1_internals_of_zone_js/code/1_4_0_9.tex}

% \texttt{ZoneDelegate}
% also declares three variables, to store the delegates zone and parent
% delegate, and to represent task counts (for each kind of task):

\texttt{ZoneDelegate} 还声明了三个变量，用来保存 delegates zone 和 parent zone，
以及表示任务的计数器（针对每种任务）：

\input{../output/1_internals_of_zone_js/code/1_4_0_10.tex}

% In
% \texttt{ZoneDelegate}
% ’s constructor, the
% \texttt{zone}
% and
% \texttt{parentDelegate}
% fields are initialized to
% the supplied parameters, and the
% \texttt{ZoneDelegate}
% and
% \texttt{ZoneSpec}
% fields for the eight
% scenarios are set (using TypeScript type guards), either to the supplied
% \texttt{ZoneSpec}
% (if
% not null), or the parent delegate’s:

在 \texttt{ZoneDelegate} 的构造函数中，
\texttt{zone} 和 \texttt{parentDelegate} 字段从提供的参数中进行初始化，
设置 \texttt{ZoneDelegate} 以及 8 个场景的 \texttt{ZoneSpec} 字段（使用 Typescript 的类型守护），
要么是 \texttt{ZoneSpec}（如果不为 null），要么是父的 delegate：

\input{../output/1_internals_of_zone_js/code/1_4_0_11.tex}

% The
% \texttt{ZoneDelegate}
% methods for the eight scenarios just forward the calls to the
% selected
% \texttt{ZoneSpec}
% (pr parent delegate) and does some house keeping. For example,
% the invoke method checks if
% \texttt{\_invokeZS}
% is defined, and if so, calls its
% \texttt{onInvoke}
% ,
% otherwise it calls the supplied callback directly:

针对 8 个场景的 \texttt{ZoneDelegate} 方法只是
将调用转发到选定的 \texttt{ZoneSpec}（父代理）并做一些内部处理。
例如，invoke 方法检查是否定义了 \texttt{\_invokeZS}，
如果是，则调用其 \texttt{onInvoke}，
否则直接调用给定的回调：

\input{../output/1_internals_of_zone_js/code/1_4_0_12.tex}

% The
% \texttt{scheduleTask}
% method is a bit different, in that it first
% 1
% tries to use the
% \texttt{\_scheduleTaskZS}
% (if defined), otherwise
% 2
% tries to use the supplied task’s
% \texttt{scheduleFn}
% (if defined), otherwise
% 3
% if a microtask calls
% \texttt{scheduleMicroTask()}
% , otherwise
% 4
% it is
% an error:

\texttt{scheduleTask} 方法有点不同，
它首先 \step{1} 尝试使用 \texttt{\_scheduleTaskZS}（如果有定义），
否则进入 \texttt{else} 分支进行一系列判断，\step{2} 尝试使用给定任务的 \texttt{scheduleFn}（如果有定义），
否则 \step{3} 如果是微任务则调用 \texttt{scheduleMicroTask})"，其它情况 \step{4} 抛出错误：

\input{../output/1_internals_of_zone_js/code/1_4_0_13.tex}

% The fork method is where new zones get created. If
% \texttt{\_forkZS}
% is defined, it is used,
% otherwise a new zone is created with the supplied
% \texttt{targetZone}
% and
% \texttt{zoneSpec}
% :

fork 方法是创建新 zone 的地方。
如果定义了 \texttt{\_forkZS}，则使用它，
否则使用给定的 \texttt{targetZone} 和 \texttt{zoneSpec} 创建一个新 zone：

\input{../output/1_internals_of_zone_js/code/1_4_0_14.tex}

% The internal variable
% \texttt{\_currentZoneFrame}
% is initialized to the root zone and
% \texttt{\_currentTask}
% to null:

内部变量 \texttt{\_currentZoneFrame} 被初始化为根 zone，\texttt{\_currentTask} 初始化为 null：

\input{../output/1_internals_of_zone_js/code/1_4_0_15.tex}
