% \subsection{platform-server/src}
\subsection{platform-server/src}

% These source files are present:

这些源文件存在：

\begin{itemize}
  \item domino\_adapter.ts
  \item http.ts
  \item location.ts
  \item platform\_state.ts
  \item server\_events.ts
  \item server\_renderer.ts
  \item server.ts
  \item styles\_host.ts
  \item tokens.ts
  \item transfer\_state.ts
  \item utils.t
  \item version.ts
\end{itemize}

% There are no sub-directories beneath src.

src 下没有子目录。

% The server.ts file declares this const:

server.ts 文件声明了这个常量：

\input{../output/10_the_platform_server_package/code/10_3_0_0.tex}

% The factory functions
% \texttt{platformServer}
% and
% \texttt{platformDynamicServer}
% create server
% platforms that use the offline template compiler and the runtime template compiler
% respectively.

工厂函数 \texttt{platformServer} 和 \texttt{platformDynamicServer}
分别创建使用离线模板编译器和运行时模板编译器的服务器平台。

% It adds two additional provider configurations. Firstly,
% \texttt{PLATFORM\_INITIALIZER}
% , which
% is an initializer function called before bootstrapping. Here we see it initializes the
% domino adapter, in a call to the local function
% \texttt{initDominoAdapter()}
% which calls
% \texttt{makeCurrent()}
% for the
% \texttt{DominoAdapter}
% :

它添加了两个额外的 provider 配置。
首先是 \texttt{PLATFORM\_INITIALIZER}，它是一个在引导前调用的初始化函数。
在这里，我们看到它在调用本地函数 \texttt{initDominoAdapter()} 中初始化 domino 适配器，
该函数为 \texttt{DominoAdapter} 调用 \texttt{makeCurrent()}：

\input{../output/10_the_platform_server_package/code/10_3_0_1.tex}

% Secondly, it adds
% \texttt{PlatformLocation}
% , which is used by applications to interact with
% location (URL) information. It is set to a class defined in location.ts,
% \texttt{ServerPlatformLocation}
% , which mostly just throws exceptions:

其次，它添加了 \texttt{PlatformLocation}，
应用使用它与 location（URL）信息进行交互。
它被设置为 location.ts 中定义的一个类，\texttt{ServerPlatformLocation}，它主要只是抛出异常：

\input{../output/10_the_platform_server_package/code/10_3_0_2.tex}

% server.ts declares two exported functions:

server.ts 声明了两个导出函数：

\input{../output/10_the_platform_server_package/code/10_3_0_3.tex}

% We saw earlier that
% \texttt{platformCore}
% is defined in:

我们之前看到 \texttt{platformCore} 定义在：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/core/src/platform_core_providers.ts}
        {<ANGULAR-MASTER>/packages/core/src/platform\_core\_providers.ts}
\end{itemize}

% as:

如下：

\input{../output/10_the_platform_server_package/code/10_3_0_4.tex}

% \texttt{platformCoreDynamic}
% adds additional provider config (for the dynamic compiler) to
% \texttt{platformCore}
% and is defined in:

\texttt{platformCoreDynamic} 向 platformCore 添加了额外的 provider 配置（用于动态编译器）并定义在：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/platform-browser-dynamic/src/platform_core_dynamic.ts}
        {<ANGULAR-MASTER>/packages/platform-browser-dynamic/src/platfrom-browser-dynamic.ts}
\end{itemize}

% as:

如下：

\input{../output/10_the_platform_server_package/code/10_3_0_5.tex}

% \texttt{createPlatformFactory()}
% is defined in:

\texttt{createPlatformFactory()} 定义在：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/core/src/application_ref.ts}
        {<ANGULAR-MASTER>/packages/core/src/application\_ref.ts}
\end{itemize}

% it calls Core’s
% \texttt{createPlatform()}
% with the supplied parameters, resulting in a new
% platform being constructed.

它使用给定的参数调用 Core 的 \texttt{createPlatform()}，从而构建一个新平台。

% The remain part of Platform-Server’s server.ts file to discuss is the definition of the
% \texttt{NgModule}
% called
% \texttt{ServerModule}
% :

Platform-Server 的 server.ts 文件的其余部分要讨论的是名为
\texttt{ServerModule} 的 \texttt{NgModule} 的定义：

\input{../output/10_the_platform_server_package/code/10_3_0_6.tex}

% The domino\_adapter.ts file create a DOM adapter for Domino. The Domino library is a
% DOM engine for HTML5 that runs in Node. Its project page is:

domino\_adapter.ts 文件为 Domino 创建一个 DOM 适配器。
Domino 库是在 Node.js 中运行的 HTML5 DOM 引擎。
它的项目主页是：

\begin{itemize}
  \item \url{https://github.com/fgnass/domino}
\end{itemize}

% and states:

并指出：

\begin{quote}
  \emph{顾名思义，domino 的目标是在 Node.js 中提供一个 DOM。}
\end{quote}

% \emph{“As the name might suggest, domino's goal is to provide a DOM in Node.”}

% The domino\_adapter.ts file provides an adapter class,
% \texttt{DominoDomAdapter}
% , based on
% Domino’s serialization functionality that implements a
% \texttt{DomAdapter}
% suitable for use in
% server environments.

domino\_adapter.ts 文件提供了一个适配器类 \texttt{DominoDomAdapter}，
它基于 Domino 的序列化功能，
它实现了一个适用于服务器环境的 \texttt{DomAdapter}。

% The domino\_adapter.ts file has these functions to parse and serialze a document:

domino adapter.ts 文件具有以下功能来解析和序列化文档：

\input{../output/10_the_platform_server_package/code/10_3_0_7.tex}

% We see
% \texttt{serializeDocument}
% being called from:

我们看到 \texttt{serializeDocument} 被调用：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/platform-server/src/platform_state.ts}
        {<ANGULAR-MASTER>/packages/platform-server/src/platform\_state.ts}
\end{itemize}

% as:

如下：

\input{../output/10_the_platform_server_package/code/10_3_0_8.tex}

% \texttt{BrowserDomAdapter}
% is defined in:

\texttt{BrowserDomAdapter} 定义在：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/platform-browser/src/browser/browser_adapter.ts}
        {<ANGULAR-MASTER>/packages/platfrom-browser/src/browser/browser\_adapter.ts}
\end{itemize}

% \texttt{DominoAdapter}
% simply extends
% \texttt{BrowserDomAdapter}
% :

\texttt{DominoAdapter} 只是简单的继承 \texttt{BrowserDomAdapter}：

\input{../output/10_the_platform_server_package/code/10_3_0_9.tex}

% Its static
% \texttt{makeCurrent()}
% method, that we saw Universal Angular uses for server-side
% rendering,  initializes those three variables and then calls
% \texttt{setRootDomAdapter()}
% :

它的静态 \texttt{makeCurrent()} 方法，
我们看到 Universal Angular 用于服务器端渲染，
初始化这三个变量，然后调用 \texttt{setRootDomAdapter()}：

\input{../output/10_the_platform_server_package/code/10_3_0_10.tex}

% Recall that
% \texttt{setRootDomAdapter()}
% is defined in:

回想一下 \texttt{setRootDomAdapter()} 定义在：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/platform-browser/src/dom/dom_adapter.ts}
        {<ANGULAR-MASTER>/packages/platform-browser/src/dom/dom\_adapter.ts}
\end{itemize}

% as:

如下：

\input{../output/10_the_platform_server_package/code/10_3_0_11.tex}

% and that
% \texttt{getDOM()}
% is used by the
% \texttt{DOMRenderer}
% . Hence our
% \texttt{DominoAdapter}
% gets wired
% into the DOM renderer.

并且 \texttt{getDOM()} 被 \texttt{DOMRenderer} 使用。
因此我们的 \texttt{DominoAdapter} 被连接到 DOM 渲染器中。

% Many of the DOM adapter methods throw exceptions as they do not make sense
% server-side:

许多 DOM 适配器方法抛出异常，因为它们在服务器端没有意义：

\input{../output/10_the_platform_server_package/code/10_3_0_12.tex}
