% \subsection{Interfaces}
\subsection{接口}

% When trying to figure out how Render3 works, a good place to start is with its
% interfaces. Let’s look at this first:

当试图弄清楚 Render3 如何工作时，一个好的开始就是它的接口。
让我们来看看这个：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/core/src/render3/interfaces/renderer.ts}
        {<ANGULAR-MASTER>/packages/core/src/render3/interfaces/renderer.ts}
\end{itemize}

% There are some simple helper interfaces describing a node, an element and a text
% node. The node is defined as have three methods to insert, append and remove a
% child:

有一些简单的辅助接口描述节点，元素和文本节点。
该节点定义为有三种方法用以插入，添加和删除一个子节点：

\input{../output/14_render_ivy_in_angular/code/14_5_2_0.tex}

% The element allows adding and removing of listeners, working with attributes and
% properties and style configuration – it is defined as:

该元素允许添加和删除侦听器，使用 attributes、properties 和样式配置 —— 它定义为：

\input{../output/14_render_ivy_in_angular/code/14_5_2_1.tex}

% The text node adds a
% \texttt{textContent}
% property:

文本节点添加了一个 \texttt{textContent} property：

\input{../output/14_render_ivy_in_angular/code/14_5_2_2.tex}

% It has this factory code. Note the return type from
% \texttt{createRenderer}
% is
% \texttt{Render3}
% 1
% –
% and that for the
% \texttt{domRendererFactory3}
% implementation
% 2
% this is the normal DOM
% \texttt{document}
% :

它有这个工厂代码。
请注意，\texttt{createRenderer} 的返回类型是 Render3 \step{1} —— 对于 \texttt{domRendererFactory3} 实现 \step{2}，
这是正常的 DOM \texttt{document}

\input{../output/14_render_ivy_in_angular/code/14_5_2_3.tex}

% This is key to moving back to regular DOM usage for code that runs in the main
% browser UI thread, and yet allowing alternatives elsewhere.
% \texttt{Renderer3}
% is a type alias:

这是在主浏览器 UI 线程中运行的代码返回到常规 DOM 使用的关键，但允许其他地方的替代方案。
\texttt{Renderer3} 是一个类型别名：

\input{../output/14_render_ivy_in_angular/code/14_5_2_4.tex}

% This represents the two kinds of renderers that are supported. The bolded text in the
% comment highlights the usage scenario for the first of these:

这表示支持的两种渲染器。
注释中的粗体文本（4 - 6 行）突出显示了其中第一个的使用场景：

\input{../output/14_render_ivy_in_angular/code/14_5_2_5.tex}

% \texttt{ProceduralRender3}
% is intended to be used from web workers and server-side:

\texttt{ProceduralRender3} 旨在用于 web workers 和服务器端：

\input{../output/14_render_ivy_in_angular/code/14_5_2_6.tex}

% Let’s now look at
% \url{view.ts}
% . It includes the following to work with static data:

现在让我们看看
\href{https://github.com/angular/angular/blob/master/packages/core/src/render3/interfaces/view.ts}
{view.ts}。
它包括以下用于处理静态数据的内容：

\input{../output/14_render_ivy_in_angular/code/14_5_2_7.tex}

% \texttt{TData}
% is defined as:

\texttt{TData} 定义如下：

\input{../output/14_render_ivy_in_angular/code/14_5_2_8.tex}

% A tree of
% \texttt{LView}
% s or
% \texttt{LContainer}
% s will be needed, so this type is a node in the
% hierarchy:

将需要 \texttt{LViews} 或 \texttt{LContainers} 树，因此该类型是层次结构中的一个节点：

\input{../output/14_render_ivy_in_angular/code/14_5_2_9.tex}

% An LView stores info relating to processing a view’s instructions. Detailed comments
% (not shown here) for each of its fields are in
% \url{thesource}
% .

\texttt{LView} 存储与处理视图指令相关的信息。
每个字段的详细注释（此处未显示）都在
\href{https://github.com/angular/angular/blob/master/packages/core/src/render3/interfaces/view.ts}
{这里}。

\input{../output/14_render_ivy_in_angular/code/14_5_2_10.tex}

% The
% \url{container.ts}
% file looks at containers, which are collections of views and sub-
% containers. It exports one type,
% \texttt{TContainer}
% :

\href{https://github.com/angular/angular/blob/0b38a039d0565cfc7beb010a87f897bece0cffde/packages/core/src/render3/interfaces/container.ts}
{container.ts}
文件查看 containers，它们是视图和子 containers 的集合。
它导出一种类型，\texttt{TContainer}

\input{../output/14_render_ivy_in_angular/code/14_5_2_11.tex}

% and one interface,
% \texttt{LContainer}
% : (note
% \url{thesourcefile}
% contained detailed comments for
% each field):

和一个接口，\texttt{LContainer}：（注
\href{https://github.com/angular/angular/blob/0b38a039d0565cfc7beb010a87f897bece0cffde/packages/core/src/render3/interfaces/container.ts}
{源文件}
包含每个字段的详细注释）：

\input{../output/14_render_ivy_in_angular/code/14_5_2_12.tex}

% The
% \url{query.ts}
% file contains the
% \texttt{QueryReadType}
% class:

\href{https://github.com/angular/angular/blob/0b38a039d0565cfc7beb010a87f897bece0cffde/packages/core/src/render3/interfaces/query.ts}
{query.ts}
文件包含 \texttt{QueryReadType} 类：

\input{../output/14_render_ivy_in_angular/code/14_5_2_13.tex}

% and the
% \texttt{LQuery}
% interface:

以及 \texttt{LQuery} 接口：

\input{../output/14_render_ivy_in_angular/code/14_5_2_14.tex}

% The
% \url{projection.ts}
% file define LProjection as:

\href{https://github.com/angular/angular/blob/0b38a039d0565cfc7beb010a87f897bece0cffde/packages/core/src/render3/interfaces/projection.ts}
{projection.ts}
文件定义 LProjection 如下：

\input{../output/14_render_ivy_in_angular/code/14_5_2_15.tex}

% The injector.ts file has this:

injector.ts 文件有这个：

\input{../output/14_render_ivy_in_angular/code/14_5_2_16.tex}

% The node.ts file is large and contains a hierarchy of node-related types.

node.ts 文件很大，包含节点相关类型的层次结构。

% The root,
% \texttt{LNode}
% , is defined (abbreviated) as:

根 \texttt{LNode} 定义（缩写）为：

\input{../output/14_render_ivy_in_angular/code/14_5_2_17.tex}

% Each of the other types adds a few additional fields to represent that node type.

其他每种类型都添加了一些额外的字段来表示该节点类型。
