\subsection{Platform-browser/src/dom}

We will sub-divide the code in the DOM sub-directory into four categories –
adapter/renderer, animation, debug and events.

We have seen how the Core package defines a rendering API and all other parts of the
Angular framework and applicaton code uses it to have content rendered. But Core
has no implementation. Now it is time to see an implementation, based on the DOM.
That is the role of these files:

\begin{itemize}
  \item shared\_styles\_host.ts
  \item util.ts
  \item dom\_adapter.ts
  \item dom\_renderer.ts
\end{itemize}

shared\_styles\_host.ts manages a set of styles.

Utils.ts contains simple string helpers:

\input{8_the_platform_browser_package/code/8_3_1_0.tex}

The two main files involved in delivering the DomRenderer are dom\_adapter.ts and
dom\_renderer.ts. A DomAdapter is a class that represents an API very close to the
HTML DOM that every web developer is familiar with. A DOM renderer is an
implementation of Core’s Rendering API in terms of a DOM adapter.

The benefit that a DomAdapter brings (compared to hard-coding calls to the actual
DOM inside a browser), is that multiple implementations of a DomAdapter can be
supplied, including in scenarios where the real DOM is not available (e.g. server-side,
or inside webworkers).

The following diagram shows how Core’s renderer API, renderer implementations and
DOM adapters are related. For many applications, the entire application will run in the
main browser UI thread and so
\texttt{BrowserDomAdapter}
will be used alongside
\texttt{DefaultDomRenderer2}
.

{ almost all methods use }

For server applications with Platform-Server, a specialist DOM adapter called
DominoAdapter will be used, and this results in content being written to an HTML file.
DominoAdapter is implemented in the Platform-Server package here:

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/platform-server/src/domino_adapter.ts}
        {<ANGULAR-MASTER>/packages/platform-server/src/domino\_adapter.ts}
\end{itemize}

It is based in this project:

\begin{itemize}
  \item \url{https://github.com/fgnass/domino}
\end{itemize}

We’ll explore this further when examining the Platform-Server package.

For more advanced browser applications that will use web workers, things are a little
more complicated and involves these main classes:
\texttt{WorkerRenderer2}
,
\texttt{MessageBasedRender2}
and
\texttt{WorkerDomAdapter}
.
\texttt{WorkerDomAdapter}
is used merely for
logging and does not place a significant part in rendering from workers. A message
broker based on a message bus exchanges messages between the web worker and
main browser UI thread.
\texttt{WorkerRenderer2}
runs in the web worker and forward all
rendering calls over the message broker to the main browser UI thread, where an
instance of
\texttt{MessageBasedRender2}
(which, despite its name, does not implement
Core’s renderer API) receives them and calls the regular
\texttt{DefaultDomRenderer2}
. We
will shortly examine in detail how rendering works with web workers. We’ll explore
rendering and web workers in the later chapter on Platform-WebWorker.

When trying to figure out how the DOM adaptor works, the best place to start is:

\begin{itemize}
  \item \href{fix: href loss url}
        {fix: href loss url}
\end{itemize}

The dom\_adapter.ts class defines the abstract
\texttt{DomAdapter}
class, the
\texttt{\_DOM}
variable
and two functions,
\texttt{getDOM()}
and
\texttt{setDOM()}
to get and set it.

\input{8_the_platform_browser_package/code/8_3_1_1.tex}

The
\texttt{DomAdapter}
class is a very long list of methods similar to what you would find a
normal DOM API (pay attention to the security warning!)– here is just a sampling:

\input{8_the_platform_browser_package/code/8_3_1_2.tex}

The dom\_renderer.ts file defines the DOM renderer that relies on
\texttt{getDOM()}
to supply
a
\texttt{DomAdapter}
. The main class it supplies is
\texttt{DomRendererFactory2}
which implements
\texttt{RendererFactory2}
. We saw earlier how
\texttt{DomRendererFactory2}
is used in the
\texttt{BROWSER\_MODULE\_PROVIDERS}
declaration, as used by
\texttt{NgModule}
:

\input{8_the_platform_browser_package/code/8_3_1_3.tex}

The
\texttt{DomRendererFactory2}
class manages a map of strings to
\texttt{Renderer2}
instances.

\input{8_the_platform_browser_package/code/8_3_1_4.tex}

Its
\texttt{createRenderer()}
method performs a switch on the encapsulation type and
returns an appropriate
\texttt{Renderer2}
:

\input{8_the_platform_browser_package/code/8_3_1_5.tex}

\texttt{DefaultDomRenderer2}
is where renderering actually occurs. It implements
\texttt{Renderer2}
. As an example, let’s look at its
\texttt{createElement()}
method:

\input{8_the_platform_browser_package/code/8_3_1_6.tex}

DOM debugging is supported via:

\begin{itemize}
  \item src/dom/debug/by.ts
  \item src/dom/debug/ng\_probe.ts
\end{itemize}

The
\texttt{By}
class may be used with Core’s
\texttt{DebugElement}
to supply predicates for its query
functions. It supplies three predicates – all, css and directive:

\input{8_the_platform_browser_package/code/8_3_1_7.tex}

DOM events are supported via:

\begin{itemize}
  \item src/dom/events/dom\_events.ts
  \item src/dom/events/event\_manager.ts
  \item src/dom/events/hammer\_common.ts
  \item src/dom/events/hammer\_gestures.ts
  \item src/dom/events/key\_events.ts
\end{itemize}

event\_manager.ts provides two classes –
\texttt{EventManager}
and
\texttt{EventManagerPlugin}
.

\texttt{EventManager}
manages an array of
\texttt{EventManagerPlugin}
s, which is defined as:

\input{8_the_platform_browser_package/code/8_3_1_8.tex}

It provides two methods to add event listeners to targets represented either by an
\texttt{HTMLElement}
or a string.
\texttt{EventManager}
itself is defined as an injectable class:

\input{8_the_platform_browser_package/code/8_3_1_9.tex}

Its constructor is defined in such a way as to allow dependency injection to inject an
array of event manager plugins. We note this list is reversed in the constructor, which
will impact the ordering of finding a plugin for an event type.

The other files in src/dom/events supply event manager plugins.

Note the comment in
\texttt{DomEventsPlugin}
:

\input{8_the_platform_browser_package/code/8_3_1_10.tex}

Touch events via the hammer project are supported via the hammer\_gesture.ts file.
The list of supported touch events are:

\input{8_the_platform_browser_package/code/8_3_1_11.tex}

This is used by
\texttt{HammerGesturesPlugin}
:

\input{8_the_platform_browser_package/code/8_3_1_12.tex}

Its
\texttt{addEventListener}
method is implemented as:

\input{8_the_platform_browser_package/code/8_3_1_13.tex}

Note the use of
\texttt{zone.runOutsideAngular()}
1
. Also note it does not implement
\texttt{addGlobalEventListener}
. Its constructor expects a
\texttt{HAMMER\_GESTURE\_CONFIG}
from
dependency injection. The Hammer package is used in the injectable
\texttt{HammerGestureConfig}
class:

\input{8_the_platform_browser_package/code/8_3_1_14.tex}

These event manager plugins need to be set in the
\texttt{NgModule}
configuration. We see
how this is done in
\texttt{BROWSER\_MODULE\_PROVIDERS}
:

\input{8_the_platform_browser_package/code/8_3_1_15.tex}
