% \subsection{router/src}
\subsection{router/src}

% The router/src directory contains:

router/src 目录包含：

\begin{itemize}
  \item apply\_redirects.ts
  \item config.ts
  \item create\_router\_state.ts
  \item create\_url\_tree.ts
  \item events.ts
  \item interfaces.ts
  \item index.ts
  \item interfaces.ts
  \item pre\_activation.ts
  \item private\_export.ts
  \item recognize.ts
  \item resolve.ts
  \item route\_reuse\_strategy.ts
  \item router\_config\_loader.ts
  \item router\_module.ts
  \item router\_outlet\_context.ts
  \item router\_preloader.ts
  \item router\_state.ts
  \item router.ts
  \item shared.ts
  \item url\_handling\_strategy.ts
  \item url\_tree.ts
  \item version.ts
\end{itemize}

% We’ll start by looking at:

我们将先查看：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/router/src/router_module.ts}
        {<ANGULAR-MASTER>/packages/router/src/router\_module.ts}
\end{itemize}

% which defines the RouterModule class and related types.

它定义了 RouterModule 类和相关类型。

% It defines three consts:

它定义了三个常量：

\input{../output/13_the_router_package/code/13_3_0_0.tex}

% The first,
% \texttt{ROUTER\_DIRECTIVES}
% , is the collection of router directives that can appear in
% Angular templates defining where the routed content is to be located on the page, and
% how links used for routing are to be displayed.
% \texttt{ROUTER\_DIRECTIVES}
% is specified in the
% declarations and exports of the
% \texttt{@NgModule}
% metadata for
% \texttt{RouterModule}
% :

第一个，\texttt{ROUTER\_DIRECTIVES} 是路由器指令的集合，
可以出现在 Angular 模板中，定义路由内容在页面上的位置，
以及如何显示用于路由的链接。
\texttt{ROUTER\_DIRECTIVES} 在 \texttt{RouterModule} 的 \texttt{@NgModule}
元数据的声明和导出中指定：

\input{../output/13_the_router_package/code/13_3_0_1.tex}

% The other two are injection tokens for DI:

另外两个是 DI 的注入令牌：

\input{../output/13_the_router_package/code/13_3_0_2.tex}

% It also defines the
% \texttt{ROUTER\_PROVIDERS}
% array of providers (which is only used by
% forRoot, not forChild):

它还定义了提供程序的 \texttt{ROUTER\_PROVIDERS} 数组（仅用于 forRoot，不用于 forChild）：

\input{../output/13_the_router_package/code/13_3_0_3.tex}

% An important provider there is
% \texttt{Router}
% , which is the actually routing service. This is set
% up in DI to return the result of the
% \texttt{setupRouter}
% factory method. An abbreviated
% version of this is as follows:

一个重要的 provider 是\texttt{Router}，这是实际的路由服务。
这是在 DI 中设置以返回 \texttt{setupRouter} 工厂方法的结果。
其缩写版本如下：

\input{../output/13_the_router_package/code/13_3_0_4.tex}

% It instantiates the router service and for each specified option / strategy takes
% appropciarte action. Then it returns the new router service instance. It is important
% that there is only a single router service per application (the web browser only have a
% single URL per session) and we need to track how this is so.

它实例化路由服务，并为每个指定的选项/策略采取适当的行动。
然后它返回新的路由服务实例。
重要的是每个应用只有一个路由服务（Web 浏览器每个会话只有一个 URL），
我们需要跟踪这是如何发生的。

% RouterModule is defined as:

RouterModule 定义如下：

\input{../output/13_the_router_package/code/13_3_0_5.tex}

% Note that both
% \texttt{forRoot}
% and
% \texttt{forChild}
% return a
% \texttt{ModuleWithProviders}
% instance. What
% they put in it is different. Recall that this type is defined in:

请注意，\texttt{forRoot} 和 \texttt{forChild} 都返回一个 \texttt{ModuleWithProviders} 实例。
他们放进去的东西不一样。
回想一下，这种类型定义在：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/core/src/metadata/ng_module.ts}
        {<ANGULAR-MASTER>/packages/core/src/metadata/ng\_module.ts}
\end{itemize}

% as follows:

如下：

\input{../output/13_the_router_package/code/13_3_0_6.tex}

% \texttt{ForChild}
% is intended for all except the root routing module. It returns
% \texttt{ngModule}
% and a
% list of providers that only contains the result of calling
% \texttt{provideRoutes}
% :

\texttt{ForChild} 适用于除根路由模块之外的所有模块。
它返回 \texttt{ngModule} 和一个
仅包含调用 \texttt{provideRoutes} 结果的 providers 列表：

\input{../output/13_the_router_package/code/13_3_0_7.tex}

% Critically, it does not contain ROUTER\_PROVIDERS. In contrast,
% \texttt{forRoot}
% adds this and
% many more providers:

重要的是，它不包含 ROUTER\_PROVIDERS。
相比之下，\texttt{forRoot} 添加了这个和更多的 providers：

\input{../output/13_the_router_package/code/13_3_0_8.tex}

% \texttt{ExtraOptions}
% are additional options passed in to
% \texttt{forRoot}
% (it is not used with
% \texttt{forChild}
% ):

\texttt{ExtraOptions} 是传递给 \texttt{forRoot} 的附加选项（它不与 \texttt{forChild} 一起使用）：

\input{../output/13_the_router_package/code/13_3_0_9.tex}

% For example, if we wished to customize how preloading worked, we need to set the
% \texttt{preloadingStrategy}
% option.

例如，如果我们希望自定义预加载的工作方式，我们需要设置 \texttt{preloadingStrategy} 选项。

% The
% \texttt{provideRouterInitializer()}
% function providers a list of initializers:

\texttt{provideRouterInitializer()} 函数提供了一个 initializers 列表：

\input{../output/13_the_router_package/code/13_3_0_10.tex}

% This uses the
% \texttt{RouterInitializer}
% class, whose purpose is best explained by this
% comment in the code:

这使用了 \texttt{RouterInitializer} 类，其目的最好通过代码中的此注释来解释：

\input{../output/13_the_router_package/code/13_3_0_11.tex}

% We saw when examining the Core package that its:

我们在检查 Core 包时看到它：

\begin{itemize}
  \item \href{https://github.com/angular/angular/blob/master/packages/core/src/application_init.ts}
        {<ANGULAR\_MASTER>/packages/core/src/application\_init.ts}
\end{itemize}

% defines
% \texttt{APP\_INITIALIZER}
% as:

将 \texttt{APP\_INITIALIZER} 定义为：

\input{../output/13_the_router_package/code/13_3_0_12.tex}

% Interfaces.ts declares a number of useful interfaces.

Interfaces.ts 声明了许多有用的接口。

\input{../output/13_the_router_package/code/13_3_0_13.tex}

% router\_config\_loader.ts defines a class -
% \texttt{RouterConfigLoader}
% – and an opaque token,
% \texttt{ROUTES}
% .  After some bookkeeping,
% \texttt{RouterConfigLoader}
% creates a new instance of
% LoadedRouterConfig it:

router\_config\_loader.ts 定义了一个类 —— \texttt{RouterConfigLoader} —— 和一个 opaque 令牌，
经过一些簿记后，\texttt{RouterConfigLoader} 创建了 LoadedRouterConfig 的一个新实例：

\input{../output/13_the_router_package/code/13_3_0_14.tex}

% The router\_state.ts file contains these classes (and some helper functions):

router\_state.ts 包含这些类（和一些辅助函数）：

\begin{itemize}
  \item RouterState
  \item ActivatedRoute
  \item ActivatedRouteSnapshot
  \item RouterStateSnapshot
\end{itemize}

% \texttt{RouterState}
% is defined as:

\texttt{RouterState} 定义为：

\input{../output/13_the_router_package/code/13_3_0_15.tex}

% \texttt{RouterStateSnapshot}
% is defined as:

\texttt{RouterStateSnapshot} 定义为：

\input{../output/13_the_router_package/code/13_3_0_16.tex}

% The
% \texttt{setRouterStateSnapshot()}
% function is defined as:

\texttt{setRouterStateSnapshot()} 函数定义为：

\input{../output/13_the_router_package/code/13_3_0_17.tex}

% So its sets the router state for the current node, and then recursively calls
% \texttt{setRouterState()}
% to set it for all children.

所以它为当前节点设置路由状态，然后递归调用 \texttt{setRouterState()} 为所有子节点设置它。

% The
% \texttt{ActivatedRoute}
% class is used by the router outlet directive to describe the
% component it has loaded:

路由器出口指令使用 \texttt{ActivatedRoute} 类来描述它已加载的组件：

\input{../output/13_the_router_package/code/13_3_0_18.tex}
